`tidyfun`

### 2019-06-09 tidyfun.Rmd
fix speakerdeck embed code in tidyfun

<script async class="speakerdeck-embed" data-id="f0d309fcbf2c4d5d9d121eee4a6144ee" data-ratio="1.77777777777778" src="//speakerdeck.com/assets/embed.js"></script>
<div style="margin-bottom:5px"> <strong> <a href="https://speakerdeck.com/jeffgoldsmith/tidyfun" title="tidyfun" target="_blank">tidyfun</a> </strong> from <strong><a href="https://speakerdeck.com/jeffgoldsmith" target="_blank">Jeff Goldsmith</a></strong>. </div><br>

>>>>

<script async class="speakerdeck-embed" data-id="1a71e0ecac2e4d7dbe07ad6d23fb6d76" data-ratio="1.77777777777778" src="//speakerdeck.com/assets/embed.js"></script>
<div style="margin-bottom:5px"> <strong> <a href="https://speakerdeck.com/jeffgoldsmith/tidyfun" title="tidyfun" target="_blank">tidyfun</a> </strong> from <strong><a href="https://speakerdeck.com/jeffgoldsmith" target="_blank">Jeff Goldsmith</a></strong>. </div><br>
